---
title: "Query a Drug"
output: html_notebook
---

<!-- Given a query Drug, DeepTarget can provide the following information:: -->
<!-- 1. Likelihood of each gene to a primary Target; Predicted Primary Target passing the threshold. -->
<!-- 2. Likelihood of each pathway to a primary MOA; Predicted Primary MOAs passing the threshold. -->
<!-- 3. Likelihood of each gene to a secondary Target; Secondary Targets passing Threshold-->
<!-- 4. Extent of Mutant Specificity of the drug to its mutant target form-->


<!-- !Input!-->
<!-- Description                       Object Name-->
<!-- corrMat -->
<!-- corrMat_FDR -->
<!-- sec_corrMat -->
<!-- sec_corrMat_P -->

<!-- Target_Mutation_specificity -->
<!-- Viability after Drug Treatment   ;onTarget$secondary_prism-->
<!-- !Output!-->
<!-- Correlation Btw viability profiles.; drugVScrispr_corr_features_list) -->
<!-- ..after CRISPR vs drug treatment                                       -->

<!-- Set the working Directory -->
```{r, setup, include=FALSE}
working_directory='/Users/sinhas8/Project_TrueTarget/'
knitr::opts_knit$set(root.dir = working_directory)
```

<!-- Uncomment this chunk to make run this script independently run -->
```{r}
# knitr::knit('Step0B_Data_and_Libraries.Rmd')
# knitr::knit('Step0_Write_Functions.Rmd')
```

```{r}
GOI='RNF5'
```
<!-- Provide the expression Distribution of the gene -->
<!-- We first test if gene of interest is expressed in at least a major proportion of cell lines -->
```{r}
cellLines_withAllData=Reduce(intersect,
                        list(colnames(onTarget$expression_20Q4),
                             colnames(onTarget$secondary_prism),
                             colnames(onTarget$avana_22Q2),
                             colnames(onTarget$mutations_matrix))
                        )
GOI_expression=onTarget$expression_20Q4[GOI,cellLines_withAllData]
GOI_expression_2plot=data.frame(GOI=GOI_expression)
ggplot(GOI_expression_2plot, aes(GOI))+
  geom_histogram()
```

```{r}
Known_Inhibitors=onTarget$drugCategory[grep(GOI,onTarget$drugCategory$target),]
Known_Inhibitors_broadTrimmed=Known_Inhibitors$broad_id_trimmed
```
<!-- DKS Score: All Dosages -->
```{r}
# corrMat; corrMat_FDR; corrMat_rank
DKS=data.frame(drugName=colnames(corrMat),
               DKS_score=corrMat[GOI,],
               DKS_rank=corrMat_rank[GOI,])
mapping_broad2common=match(DKS$drugName, onTarget$drugCategory$broad_id_trimmed)
DKS$drugName_common=onTarget$drugCategory$name[mapping_broad2common]
DKS$KnownTarget=onTarget$drugCategory$target[mapping_broad2common]
DKS$KnownMOA=onTarget$drugCategory$moa[mapping_broad2common]
DKS[order(DKS$DKS_rank),]
```
<!-- DKS Score: One Dosages -->
```{r}
# corrMat_1dose; corrMat_P_1dose; corrMat_rank_1dose
DKS_1dose=data.frame(drugName=colnames(corrMat_1dose),
               DKS_score=corrMat_1dose[GOI,],
               DKS_rank=corrMat_rank_1dose[GOI,])
mapping_broad2common=match(DKS_1dose$drugName,
                           onTarget$drugCategory$broad_id_trimmed)
DKS_1dose$drugName_common=onTarget$drugCategory$name[mapping_broad2common]
DKS_1dose$KnownTarget=onTarget$drugCategory$target[mapping_broad2common]
DKS_1dose$KnownMOA=onTarget$drugCategory$moa[mapping_broad2common]
DKS_1dose=DKS_1dose[order(DKS_1dose$DKS_score, decreasing = T),]
DKS_1dose$HitRank=1:nrow(DKS_1dose)
DKS_1dose
tableS1=head(DKS_1dose, 2)
# write.table(tableS1[,c(4,2,3,5,6)], file = 'Data/TableS1_Drugs_for_FIBP_by_DeepTarget.tsv', sep = '\t')
write.table(tableS1[,c(4,2,3,5,6)], file = 'Data/TableS1_Drugs_for_RNF5_by_DeepTarget.tsv', sep = '\t')
```
<!-- Where does the known inhibitor ranks -->
```{r}
DKS_1dose[DKS_1dose$drugName %in% Known_Inhibitors$broad_id_trimmed,]
dim(DKS_1dose)
```

<!-- Find other drugs like known Inhibitors -->
```{r}
library("Hmisc")
prism_cor <- rcorr(as.matrix(t(onTarget$drug_prism)))
Similarity2_otherdrugs=prism_cor$r[Known_Inhibitors$broad_id_trimmed,]
top10Hits=head(Similarity2_otherdrugs[order(Similarity2_otherdrugs, decreasing = T)], 10)
DDS_Score=onTarget$drugCategory[match(names(top10Hits), onTarget$drugCategory$broad_id_trimmed),]
TableS2=data.frame(drugName=DDS_Score[,3],DDS_Score=top10Hits,DDS_Score[,c(5, 6)])
write.table(TableS2, file = 'Data/TableS2_CitrinReport.tsv', sep = '\t')
```

```{r}
DKS_1dose[DKS_1dose$drugName %in% rownames(TableS2),]
onTarget$drugCategory[grep('solute',onTarget$drugCategory$moa),]
onTarget$drugCategory[grep('SLC25',onTarget$drugCategory$target),]
```


```{r}
sec_corrMat
sec_corrMat_P
```

```{r}
Target_Mutation_specificity
```
Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

