---
title: "Query a Drug"
output: html_notebook
---

<!-- Given a query Drug, DeepTarget can provide the following information:: -->
<!-- 1. Likelihood of each gene to a primary Target; Predicted Primary Target passing the threshold. -->
<!-- 2. Likelihood of each pathway to a primary MOA; Predicted Primary MOAs passing the threshold. -->
<!-- 3. Likelihood of each gene to a secondary Target; Secondary Targets passing Threshold-->
<!-- 4. Extent of Mutant Specificity of the drug to its mutant target form-->


<!-- !Input!-->
<!-- Description                       Object Name-->
<!-- corrMat -->
<!-- corrMat_FDR -->
<!-- sec_corrMat -->
<!-- sec_corrMat_P -->

<!-- Target_Mutation_specificity -->
<!-- Viability after Drug Treatment   ;onTarget$secondary_prism-->
<!-- !Output!-->
<!-- Correlation Btw viability profiles.; drugVScrispr_corr_features_list) -->
<!-- ..after CRISPR vs drug treatment                                       -->

<!-- Set the working Directory -->
```{r, setup, include=FALSE}
working_directory='/Users/sinhas8/Project_TrueTarget/'
knitr::opts_knit$set(root.dir = working_directory)
```

<!-- Uncomment this chunk to make run this script independently run -->
```{r}
# knitr::knit('Step0B_Data_and_Libraries.Rmd')
# knitr::knit('Step0_Write_Functions.Rmd')
```

```{r}
corrMat
corrMat_FDR
corrMat_rank

corrMat_1dose
corrMat_P_1dose
corrMat_rank_1dose

sec_corrMat
sec_corrMat_P
Target_Mutation_specificity
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

