---
title: "R Notebook"
output: html_notebook
---

<!-- Load the needed data -->
```{r}
require(magrittr)
require('tidyverse')
onTarget=readRDS('/Users/sinhas8/Project_TrueTarget/Data/onTarget_v12.RDS')
CRISPR22Q2=read.csv('/Users/sinhas8/Downloads/CRISPR_gene_effect.csv')
```
Load needed functions
```{r}
source('/Users/sinhas8/Project_TrueTarget/Tools/myCustom_functions.R')
```

```{r, tidy = TRUE}
CRISPR22Q2 <- CRISPR22Q2 %>% set_rownames(.$DepMap_ID) %>% select(-1)
colnames(CRISPR22Q2) <- strsplit_customv0(colnames(CRISPR22Q2), infunc_split_by = '\\.')
onTarget$avana_22Q2 <- CRISPR22Q2
saveRDS(onTarget, '/Users/sinhas8/Project_TrueTarget/Data/onTarget_v2.0.RDS')
```

```{r}
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

