---
title: " Atomic inputs needed for DeepTarget"
output: html_notebook
---

<!-- Set the working Directory -->
```{r, setup, include=FALSE}
working_directory='/Users/sinhas8/Project_TrueTarget/'
knitr::opts_knit$set(root.dir = working_directory)
```

<!-- Loading Libraries -->
```{r}
packages_required<-c('parallel','tictoc','fgsea', 'ggplot2', 'ggpubr',
                     'statar', 'interactions','stats', 'reshape2', 'pROC',
                     'data.table','ggrepel', 'grid','cowplot','gridExtra',
                     'stringb', 'DEGreport', 'readxl', 'stringr')

installORload(packages_required)
installORload.bioc(packages_required)
```
<!-- Load the necessary Data for to execute any data-->
<!-- Download this data using the following link -->
```{r}
onTarget=readRDS('Data/onTarget_v3.0.RDS')
# onTarget is the most important piece in the DeepTarget Framework
# It is a list of Data.frames with the following data
#                                 Length    Class      Mode     Description
# drugsCommonName                      4686 factor     numeric  Commonly used Drug Names
# Annotated_Target                     4686 factor     numeric  Known Targets of above drugs from Drugbank
# broad_id                             4686 -none-     character Broad designated unique Drug id (all screens use this ID)
# avana                            11458125 -none-     numeric  CRISPR KO profile of ~800 cell lines for 20K genes
# mutations_matrix                 30979350 -none-     numeric  Mutation binary matrix for ~2K cell lines; 0 is WT; 1 is mutated
# achilles                         12272081 -none-     numeric  shRNA KO profile of ~800 cell lines for 20K genes
# drug_prism                        2708508 -none-     numeric  Drug Treatment profile of ~5K drugs in 500 cell lines; 1 dosage
# drugCategory                            8 data.frame list     Metadata on drugs
# secondary_prism                    789584 -none-     numeric  Drug Treatment profile of ~5K drugs in 500 cell lines; AUC across 8 dosages
# annotation_20Q4                        26 data.frame list     Metadata of cellines
# expression_20Q4                  26394432 -none-     numeric  Expression profile of ~2K cell lines for 20K genes
# secondary_screen_drugAnnotation         4 data.frame list     Metadata of secondary Screen with 8 dosages
# secondary_prism_ic50               789584 -none-     numeric  secondary screen where drug response is measured using ic50 instead of AUC

#!* Describe the dataset below
KnownTarget_predictions=readRDS('Data/KnownTarget_predictions_v4.RDS')
drugCandidates_for_secTargets=readRDS('Data/drugCandidates_for_secTargets.RDS')
drugVScrispr_corr_features_list=readRDS('Data/drugVScrispr_corr_features_list.RDS')
drugVScrispr_corr_features_list_secondary=readRDS('/Users/sinhas8/Project_TrueTarget/Data/drugVScrispr_corr_features_list_secondary.RDS')
human_Kinases=read_xlsx('Data/human_Kinases.xlsx')
```
<!-- Preprocessing -->
<!-- Creating dataframes that would be required during analysis -->
```{r}
# <!-- Defining the cormat strength, Pvalue and the rank to save in known target prediction-->
drugVScrispr_corr_Strength=sapply(drugVScrispr_corr_features_list, function(x) x[,2])
corrMat_P=sapply(drugVScrispr_corr_features_list, function(x) x[,1])
corrMat=drugVScrispr_corr_Strength
corrMat_rank=apply(-corrMat, 2, rank)

#corrmat-Z
#Z-score in the first possible way.
corrMat_z=apply(corrMat, 2, scale)
rownames(corrMat_z)=rownames(corrMat)
corrMat_log10P=-log10(corrMat_P)
corrMat_bothMAGandP=corrMat_log10P*corrMat_z

#Add Secondary-DKS score
sec_corrMat=do.call(cbind, sapply(drugVScrispr_corr_features_list_secondary, function(x) err_handle(x[,2])))
sec_corrMat_P=do.call(cbind, sapply(drugVScrispr_corr_features_list_secondary, function(x) err_handle(x[,1])))
sec_corrMat_rank=apply(-sec_corrMat, 2, rank)

# <!-- Compute if a drug is inhibitor or not -->
category_inhibitor=c('inhibitor', 'antagonist', 'blocker')
category_activator=c('agonist', 'activator', 'stimulant')
category_inhibitor_drugs_ID=sapply(category_inhibitor, function(x) grep(x, onTarget$drugCategory$moa))
category_activator_drugs_ID=sapply(category_activator, function(x) grep(x, onTarget$drugCategory$moa))
category_inhibitor_drugs_ID=unique(unlist(category_inhibitor_drugs_ID))
category_activator_drugs_ID=unique(unlist(category_activator_drugs_ID))
onTarget$drugCategory$is.inhibitor=F
onTarget$drugCategory$is.inhibitor[category_inhibitor_drugs_ID]=T
onTarget$drugCategory$is.activator=F
onTarget$drugCategory$is.activator[category_activator_drugs_ID]=T

# <!-- create matrix of drug, crispr and expression with the matched cell lines -->
matched_cellLines=Reduce(intersect,
                         list(colnames(onTarget$expression_20Q4),
                              colnames(onTarget$avana_22Q2),
                              colnames(onTarget$secondary_prism)))
expression_matched=onTarget$expression_20Q4[,matched_cellLines]
avana_matched=onTarget$avana_22Q2[,matched_cellLines]
drug_matched=onTarget$secondary_prism[,matched_cellLines]
```
Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.