---
title: " Atomic inputs needed for DeepTarget"
output: html_notebook
---

<!-- Set the working Directory -->
```{r, setup, include=FALSE}
working_directory='/Users/sinhas8/Project_TrueTarget/'
knitr::opts_knit$set(root.dir = working_directory)
```

<!-- This code ensures that all required packages are installed and available for use in the script, allowing the user to run the script without encountering any errors related to missing packages. -->
<!-- It installs or loads a list of required R packages. The packages_required variable is a character vector containing the names of the packages that are needed for the script to run properly. The installORload function is then used to install any packages that are not already installed on the user's system. The installORload.bioc function is used to install any Bioconductor packages that are not already installed. -->
```{r}
packages_required<-c('parallel','tictoc','fgsea', 'ggplot2', 'ggpubr',
                     'statar', 'interactions','stats', 'reshape2', 'pROC',
                     'data.table','ggrepel', 'grid','cowplot','gridExtra',
                     'stringb', 'DEGreport', 'readxl', 'stringr')

installORload(packages_required)
installORload.bioc(packages_required)
```
<!-- This code loads the necessary data for the script to run properly. It uses the readRDS function to read in four RDS files containing the data that the script will use. The names of the files and the data they contain are: -->
<!-- onTarget_v3.0.RDS: This file contains the main data object used by the DeepTarget framework. It is a list of data frames with various data on drugs, cell lines, and gene expression. -->
<!-- KnownTarget_predictions_v4.RDS: This file contains metadata on drugs and their known and predicted targets. -->
<!-- drugVScrispr_corr_features_list.RDS: This file contains DKS scores and p-values for each gene versus each drug. -->
<!-- drugVScrispr_corr_features_list_secondary.RDS: This file contains secondary DKS scores and p-values for each gene versus each drug. -->
<!-- The read_xlsx function is also used to read in an Excel file containing a list of all human kinases genes.-->
```{r}
onTarget=readRDS('Data/onTarget_v3.0.RDS')
# It is a list of Data.frames with the following data
#                                 Length    Class      Mode     Description
# drugsCommonName                      4686 factor     numeric  Commonly used Drug Names
# Annotated_Target                     4686 factor     numeric  Known Targets of above drugs from Drugbank
# broad_id                             4686 -none-     character Broad designated unique Drug id (all screens use this ID)
# avana                            11458125 -none-     numeric  CRISPR KO profile of ~800 cell lines for 20K genes
# mutations_matrix                 30979350 -none-     numeric  Mutation binary matrix for ~2K cell lines; 0 is WT; 1 is mutated
# achilles                         12272081 -none-     numeric  shRNA KO profile of ~800 cell lines for 20K genes
# drug_prism                        2708508 -none-     numeric  Drug Treatment profile of ~5K drugs in 500 cell lines; 1 dosage
# drugCategory                            8 data.frame list     Metadata on drugs
# secondary_prism                    789584 -none-     numeric  Drug Treatment profile of ~5K drugs in 500 cell lines; AUC across 8 dosages
# annotation_20Q4                        26 data.frame list     Metadata of cellines
# expression_20Q4                  26394432 -none-     numeric  Expression profile of ~2K cell lines for 20K genes
# secondary_screen_drugAnnotation         4 data.frame list     Metadata of secondary Screen with 8 dosages
# secondary_prism_ic50               789584 -none-     numeric  secondary screen where drug response is measured using ic50 instead of AUC

#!* Describe the dataset below
# Metadata of Drugs and their target+DeepTarget's top predicted target information 
KnownTarget_predictions=readRDS('Data/KnownTarget_predictions_v4.RDS')
# DKS Score & P for each gene vs each drug. 
drugVScrispr_corr_features_list=readRDS('Data/drugVScrispr_corr_features_list.RDS')
# Secondary DKS Score & P for each gene vs each drug.
drugVScrispr_corr_features_list_secondary=readRDS('/Users/sinhas8/Project_TrueTarget/Data/drugVScrispr_corr_features_list_secondary.RDS')
# drugCandidates_for_secTargets=readRDS('Data/drugCandidates_for_secTargets.RDS')
# List of all Human Kinases genes
human_Kinases=read_xlsx('Data/human_Kinases.xlsx')
```
<!-- This code performs some preprocessing steps on the data. It first defines some variables for the DKS scores, p-values, and ranks of the genes versus drugs -->
<!-- Creating dataframes that would be required during analysis -->
```{r}
# <!-- Defining the cormat strength, Pvalue and the rank to save in known target prediction-->
drugVScrispr_corr_Strength=sapply(drugVScrispr_corr_features_list, function(x) x[,2])
corrMat_P=sapply(drugVScrispr_corr_features_list, function(x) x[,1])
corrMat=drugVScrispr_corr_Strength
corrMat_rank=apply(-corrMat, 2, rank)

# Next, the code computes the Z-scores for the DKS scores and combines them with the log10-transformed p-values to create a matrix of both magnitude and p-values. The secondary DKS scores are also added to this matrix.
#Z-score in the first possible way.
corrMat_z=apply(corrMat, 2, scale)
rownames(corrMat_z)=rownames(corrMat)
corrMat_log10P=-log10(corrMat_P)
corrMat_bothMAGandP=corrMat_log10P*corrMat_z

#Add Secondary-DKS score
sec_corrMat=do.call(cbind, sapply(drugVScrispr_corr_features_list_secondary, function(x) err_handle(x[,2])))
sec_corrMat_P=do.call(cbind, sapply(drugVScrispr_corr_features_list_secondary, function(x) err_handle(x[,1])))
sec_corrMat_rank=apply(-sec_corrMat, 2, rank)

# We then define which drugs are inhibitors or activators based on their mechanism of action (MOA). This is done by using the grep function to find the MOA categories that contain the keywords 'inhibitor', 'antagonist', 'blocker', 'agonist', 'activator', and 'stimulant'. The resulting drug IDs are then used to create new columns in the onTarget$drugCategory data frame indicating whether a drug is an inhibitor or activator.
# <!-- Compute if a drug is inhibitor or not -->
category_inhibitor=c('inhibitor', 'antagonist', 'blocker')
category_activator=c('agonist', 'activator', 'stimulant')
category_inhibitor_drugs_ID=sapply(category_inhibitor, function(x) grep(x, onTarget$drugCategory$moa))
category_activator_drugs_ID=sapply(category_activator, function(x) grep(x, onTarget$drugCategory$moa))
category_inhibitor_drugs_ID=unique(unlist(category_inhibitor_drugs_ID))
category_activator_drugs_ID=unique(unlist(category_activator_drugs_ID))
onTarget$drugCategory$is.inhibitor=F
onTarget$drugCategory$is.inhibitor[category_inhibitor_drugs_ID]=T
onTarget$drugCategory$is.activator=F
onTarget$drugCategory$is.activator[category_activator_drugs_ID]=T

# Finally, we create matrices of gene expression, CRISPR knockout data, and drug treatment data for only the cell lines that are common to all three datasets. This allows us to perform analyses on only the cell lines that have data available for all three types of data.
matched_cellLines=Reduce(intersect,
                         list(colnames(onTarget$expression_20Q4),
                              colnames(onTarget$avana_22Q2),
                              colnames(onTarget$secondary_prism)))
expression_matched=onTarget$expression_20Q4[,matched_cellLines]
avana_matched=onTarget$avana_22Q2[,matched_cellLines]
drug_matched=onTarget$secondary_prism[,matched_cellLines]
```
Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.